SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
Acta paper: minor clean-up so that the paper compiles without errors

\begin{proof}
%  Let $pn=<...>$ be a pNet. The set of states 
%  managed by the two algorithms both are subsets of the cartesian
%  product of the pLTS states, as defined in \pageref{def-states}. In a
%  similar way, the set of state variables are also equal. Comparing
%  transitions requires a little more care, because within the
%  MakeTransitions function, fresh variables are created everytime a
%  synchronisation vector is used (this occurs within the $MkPred$ and
%  $matching$ functions). However, given a global state, the call of
%  $MakeTransitions$ will always returns exactly the same set of OTs, up to
%  renaming of these fresh variables\footnote{I think this does not
%    need any specific proof, given that it is the same function,
%    called with the same arguments}.
%
%  Let us define the following sets of OTs, as computed by the 2
%  algorithms:
%  \ERIC{not sure whether all these sets are useful, but it's good to
%    have them precisely defined for the moment}
%  \begin{itemize}
%    \item $L1$ = original set of transitions by Algorithm 1
%      (i.e. before line 11), 
%    \item $L1-sat$ = original set of transitions by Algorithm 1, after
%      satisfiability check (i.e. after line 11),
%    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
%      by line 12.
%    \item $L2-sat$ = original set of transitions by Algorithm 2
%      (i.e. before line 13), 
%    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
%          by line 13.
%  \end{itemize}
%
%  For each of these, define $States : OT^* -> State^*$ the function
%  computing the set of target states of a set of OTs.
%
%  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
%  variables) and $States(L1-reach) = States(L2-reach)$.
%
%  From the structure of the main loops of the algorithms, we know that
%  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
%  States(L2-sat)$.
%  \qed
%\end{proof}
%  
%    \medskip
%  \noteInEM{I keep below the original proof draft from Xudong, though
%    I'm not sure if parts of it can be reused}
\begin{proof of Theorem \ref{Th:CorrectnessWithoutAssignments}}

@@

From the structure of the main loop of the algorithms, we can get $States(L2_{reach})\subseteq  States(L1)$, then
\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
\noteInEric{I don't agree with the previous statement: the main loop
  constructs L1 (resp $L2_{sat}$), note the sets of states, so this
  argument would give you

>>>>

%\begin{proof}
%  Let $pn=<...>$ be a pNet. The set of states 
%  managed by the two algorithms both are subsets of the cartesian
%  product of the pLTS states, as defined in \pageref{def-states}. In a
%  similar way, the set of state variables are also equal. Comparing
%  transitions requires a little more care, because within the
%  MakeTransitions function, fresh variables are created everytime a
%  synchronisation vector is used (this occurs within the $MkPred$ and
%  $matching$ functions). However, given a global state, the call of
%  $MakeTransitions$ will always returns exactly the same set of OTs, up to
%  renaming of these fresh variables\footnote{I think this does not
%    need any specific proof, given that it is the same function,
%    called with the same arguments}.
%
%  Let us define the following sets of OTs, as computed by the 2
%  algorithms:
%  \ERIC{not sure whether all these sets are useful, but it's good to
%    have them precisely defined for the moment}
%  \begin{itemize}
%    \item $L1$ = original set of transitions by Algorithm 1
%      (i.e. before line 11), 
%    \item $L1-sat$ = original set of transitions by Algorithm 1, after
%      satisfiability check (i.e. after line 11),
%    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
%      by line 12.
%    \item $L2-sat$ = original set of transitions by Algorithm 2
%      (i.e. before line 13), 
%    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
%          by line 13.
%  \end{itemize}
%
%  For each of these, define $States : OT^* -> State^*$ the function
%  computing the set of target states of a set of OTs.
%
%  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
%  variables) and $States(L1-reach) = States(L2-reach)$.
%
%  From the structure of the main loops of the algorithms, we know that
%  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
%  States(L2-sat)$.
%  \qed
%\end{proof}
%  
%    \medskip
%  \noteInEM{I keep below the original proof draft from Xudong, though
%    I'm not sure if parts of it can be reused}
\begin{proof}[Theorem \ref{Th:CorrectnessWithoutAssignments}]

@@

From the structure of the main loop of the algorithms, we can get $States(L2_{reach})\subseteq  States(L1)$, then
\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
\noteInEM{I don't agree with the previous statement: the main loop
  constructs L1 (resp $L2_{sat}$), note the sets of states, so this
  argument would give you }
